Fifteen years of decentralization attempts

### 2014-03-20 paper.tex
Current system fixes
Freenet fixes

	Many other decentralized peer-to-peer networks have been proposed and some have been implemented \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}. Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan. Each of these decentralized networks will be discussed in the next section. Note that we're only considering fully decentralized networks here. Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.

@@

		There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file. Another key is the Signed-Subspace key (SSK) which enables personal namespaces. This key contains a public key and a private key where the private key is used to store the data and the public key is used in the queries of the file. The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.

		The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network. Each peer has only knowledge about his neighbours. Each request has a Hops-To-Live timer which indicates how many peers the request may traversal. Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more. Results of queries are being cached in intermediate nodes to reduce the time for a query response. To prevent looping of the requests, each request contains a random identifier. The peers the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.

>>>>

	Many other decentralized peer-to-peer networks have been proposed and some have been implemented \cite{mislove2004ap3, rennhard2002introducing, panchenko2006nisan, rowstron2001pastry, nambiar2006salsa, freedman2002tarzan, ripeanu2001peer, androutsellis2004survey}. Examples of fully decentralized networks are Gnutella, Freenet, Pastry, Tapestry, and Tarzan. Each of these decentralized networks will be discussed in the next section. Note that we're only considering fully decentralized networks here, with the exception of Torsk (which is almost fully decentralized but still requires a Neighbourhood Authority). Networks that are partially or hybrid centralized, such as KaZaA or Napster, are not discussed here.

@@

		There are three types of file keys in Freenet: the first one is called the Keyword-Signed Key (KSK) which is derived from a short description of the file. Another key is the Signed-Subspace key (SSK) which enables personal namespaces. This key contains a public and a private key. The private key is used to store the data and the public key is used in the queries for the file. The third type of key is the Content-Hash Key (CHK) which is used for updating and splitting of contents.

		The routing algorithm for storing and retrieving data is dynamically and can adjust to the topology of the network. Each peer has only knowledge about his neighbours. Each request has a Hops-To-Live timer which indicates how many peers the request may traversal. Each peer decrements the timer by one and when the timer reaches zero, the request isn't forwarded any more. Results of queries are being cached in intermediate nodes to reduce the time for a query response. To prevent looping of the requests, each request contains a random identifier. The peers that the request travels through, keep track of these identifiers and rejects the request if the request has already been answered by the peer.
